\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-09-01 ecology_and_evolution/paper.tex
renamed folder

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyverse)}
\FunctionTok{library}\NormalTok{(lubridate)}
\FunctionTok{library}\NormalTok{(sf)}
\FunctionTok{library}\NormalTok{(patchwork)}
\FunctionTok{library}\NormalTok{(forestecology)}
\FunctionTok{library}\NormalTok{(blockCV)}

\CommentTok{\# Resolve conflicting functions}
\NormalTok{filter }\OtherTok{\textless{}{-}}\NormalTok{ dplyr}\SpecialCharTok{::}\NormalTok{filter}
\NormalTok{select }\OtherTok{\textless{}{-}}\NormalTok{ dplyr}\SpecialCharTok{::}\NormalTok{select}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{census\_2013\_scbi }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"scbi.stem2.csv"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(stemID, sp, }\AttributeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# Convert date from character to date}
    \AttributeTok{date =} \FunctionTok{mdy}\NormalTok{(date),}
    \CommentTok{\# Convert dbh to be in cm}
    \AttributeTok{dbh =} \FunctionTok{as.numeric}\NormalTok{(dbh) }\SpecialCharTok{/} \DecValTok{10}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(gx }\SpecialCharTok{\textless{}} \DecValTok{300}\NormalTok{, }\FunctionTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census\_2018\_scbi }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"scbi.stem3.csv"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(stemID, sp, }\AttributeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{date =} \FunctionTok{mdy}\NormalTok{(date),}
    \AttributeTok{dbh =} \FunctionTok{as.numeric}\NormalTok{(dbh) }\SpecialCharTok{/} \DecValTok{10}
\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(gx }\SpecialCharTok{\textless{}} \DecValTok{300}\NormalTok{, }\FunctionTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth\_scbi }\OtherTok{\textless{}{-}} \FunctionTok{compute\_growth}\NormalTok{(}\AttributeTok{census\_1 =}\NormalTok{ census\_2013\_scbi, }\AttributeTok{census\_2 =}\NormalTok{ census\_2018\_scbi }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{filter}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{str\_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\AttributeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{select}\NormalTok{(stemID, sp, dbh1, dbh2, growth, geometry)}
\DocumentationTok{\#\# Simple feature collection with 7954 features and 5 fields}
\DocumentationTok{\#\# Geometry type: POINT}
\DocumentationTok{\#\# Dimension:     XY}
\DocumentationTok{\#\# Bounding box:  xmin: 0.2 ymin: 300 xmax: 300 ymax: 600}
\DocumentationTok{\#\# CRS:           NA}
\DocumentationTok{\#\# \# A tibble: 7,954 x 6}
\DocumentationTok{\#\#   stemID sp     dbh1  dbh2 growth   geometry}
\DocumentationTok{\#\#    \textless{}dbl\textgreater{} \textless{}fct\textgreater{} \textless{}dbl\textgreater{} \textless{}dbl\textgreater{}  \textless{}dbl\textgreater{}    \textless{}POINT\textgreater{}}
\DocumentationTok{\#\# 1      4 nysy  13.6   14.2  0.103 (14.2 428)}
\DocumentationTok{\#\# 2      5 havi   8.8    9.6  0.150  (9.4 436)}
\DocumentationTok{\#\# 3      6 havi   3.25   4    0.140  (1.3 434)}
\DocumentationTok{\#\# 4     77 qual  65.2   66    0.141 (34.7 307)}
\DocumentationTok{\#\# 5     79 tiam  47.7   46.8 {-}0.161   (40 381)}
\DocumentationTok{\#\# \# ... with 7,949 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ggplot}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_sf}\NormalTok{(}\AttributeTok{data =}\NormalTok{ growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{sample\_n}\NormalTok{(}\DecValTok{500}\NormalTok{), }\FunctionTok{aes}\NormalTok{(}\AttributeTok{size =}\NormalTok{ growth)) }\SpecialCharTok{+} \FunctionTok{scale\_size\_binned}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{,}
    \DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{size =} \FunctionTok{expression}\NormalTok{(}\FunctionTok{paste}\NormalTok{(Growth, }\StringTok{" (cm "}\NormalTok{, y}\SpecialCharTok{\^{}}\NormalTok{\{}
    \SpecialCharTok{{-}}\DecValTok{1}
\NormalTok{\}, }\StringTok{")"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sp\_info }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"SCBI\_ForestGEO\_sp\_ecology.csv"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{select}\NormalTok{(}\AttributeTok{sp =}\NormalTok{ spcode, family, genus, species, canopy\_position, drought\_tolerance)}
\NormalTok{sp\_info}
\DocumentationTok{\#\# \# A tibble: 65 x 6}
\DocumentationTok{\#\#   sp    family        genus       species     canopy\_position drought\_toleran\textasciitilde{}}
\DocumentationTok{\#\#   \textless{}chr\textgreater{} \textless{}chr\textgreater{}         \textless{}chr\textgreater{}       \textless{}chr\textgreater{}       \textless{}chr\textgreater{}           \textless{}chr\textgreater{}           }
\DocumentationTok{\#\# 1 acne  Sapindaceae   Acer        negundo     understory      drought{-}resista\textasciitilde{}}
\DocumentationTok{\#\# 2 acpl  Sapindaceae   Acer        platanoides canopy          drought{-}resista\textasciitilde{}}
\DocumentationTok{\#\# 3 acru  Sapindaceae   Acer        rubrum      canopy          drought{-}resista\textasciitilde{}}
\DocumentationTok{\#\# 4 aial  Simaroubaceae Ailanthus   altissima   canopy          drought{-}resista\textasciitilde{}}
\DocumentationTok{\#\# 5 amar  Rosaceae      Amelanchier arborea     understory      drought{-}resista\textasciitilde{}}
\DocumentationTok{\#\# \# ... with 60 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth\_scbi }\OtherTok{\textless{}{-}}\NormalTok{ growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{left\_join}\NormalTok{(sp\_info, }\AttributeTok{by =} \StringTok{"sp"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{sp =} \FunctionTok{as.factor}\NormalTok{(sp))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Install development version of allodb using:}
\CommentTok{\# remotes::install\_github("forestgeo/allodb")}
\FunctionTok{library}\NormalTok{(allodb)}
\NormalTok{growth\_scbi }\OtherTok{\textless{}{-}}\NormalTok{ growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# Compute basal area:}
    \AttributeTok{basal\_area =} \FloatTok{0.0001} \SpecialCharTok{*}\NormalTok{ pi }\SpecialCharTok{*}\NormalTok{ (dbh1 }\SpecialCharTok{/} \DecValTok{2}\NormalTok{)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
    \CommentTok{\# Compute above ground biomass:}
    \AttributeTok{agb =} \FunctionTok{get\_biomass}\NormalTok{(}
      \AttributeTok{dbh =}\NormalTok{ dbh1,}
      \AttributeTok{genus =}\NormalTok{ genus,}
      \AttributeTok{species =}\NormalTok{ species,}
      \AttributeTok{coords =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{78.2}\NormalTok{, }\FloatTok{38.9}\NormalTok{)}
\NormalTok{    )}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Define competitive distance range}
\NormalTok{comp\_dist }\OtherTok{\textless{}{-}} \FloatTok{7.5}

\CommentTok{\# Manually construct study region boundary}
\NormalTok{study\_region\_scbi }\OtherTok{\textless{}{-}} \FunctionTok{tibble}\NormalTok{(}\AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{), }\AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{,}
    \DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{sf\_polygon}\NormalTok{()}

\NormalTok{growth\_scbi }\OtherTok{\textless{}{-}}\NormalTok{ growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{add\_buffer\_variable}\NormalTok{(}\AttributeTok{size =}\NormalTok{ comp\_dist, }\AttributeTok{region =}\NormalTok{ study\_region\_scbi)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Manually define spatial blocks to act as folds}
\NormalTok{n\_fold }\OtherTok{\textless{}{-}} \DecValTok{4}
\NormalTok{fold1 }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{0}\NormalTok{), }\FunctionTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold2 }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{150}\NormalTok{), }\FunctionTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold3 }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{0}\NormalTok{), }\FunctionTok{c}\NormalTok{(}\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold4 }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{150}\NormalTok{), }\FunctionTok{c}\NormalTok{(}\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{blocks\_scbi }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}\FunctionTok{sf\_polygon}\NormalTok{(fold1), }\FunctionTok{sf\_polygon}\NormalTok{(fold2), }\FunctionTok{sf\_polygon}\NormalTok{(fold3),}
    \FunctionTok{sf\_polygon}\NormalTok{(fold4)) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{folds =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\NormalTok{n\_fold) }\SpecialCharTok{\%\textgreater{}\%}
        \FunctionTok{factor}\NormalTok{())}

\CommentTok{\# Associate each observation to a fold}
\NormalTok{spatial\_block\_scbi }\OtherTok{\textless{}{-}} \FunctionTok{spatialBlock}\NormalTok{(}\AttributeTok{speciesData =}\NormalTok{ growth\_scbi, }\AttributeTok{k =}\NormalTok{ n\_fold,}
    \AttributeTok{selection =} \StringTok{"systematic"}\NormalTok{, }\AttributeTok{blocks =}\NormalTok{ blocks\_scbi, }\AttributeTok{showBlocks =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{verbose =} \ConstantTok{FALSE}\NormalTok{)}

\NormalTok{growth\_scbi }\OtherTok{\textless{}{-}}\NormalTok{ growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{foldID =}\NormalTok{ spatial\_block\_scbi}\SpecialCharTok{$}\NormalTok{foldID }\SpecialCharTok{\%\textgreater{}\%}
        \FunctionTok{factor}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ggplot}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_sf}\NormalTok{(}\AttributeTok{data =}\NormalTok{ blocks\_scbi, }\AttributeTok{fill =} \StringTok{"transparent"}\NormalTok{, }\AttributeTok{linetype =} \StringTok{"dashed"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{geom\_sf\_text}\NormalTok{(}\AttributeTok{data =}\NormalTok{ growth\_scbi }\SpecialCharTok{\%\textgreater{}\%}
        \FunctionTok{sample\_n}\NormalTok{(}\DecValTok{1000}\NormalTok{), }\FunctionTok{aes}\NormalTok{(}\AttributeTok{label =}\NormalTok{ foldID, }\AttributeTok{col =}\NormalTok{ buffer))}
\end{Highlighting}
\end{Shaded}

@@

\caption{Schematic of spatial cross-validation. Using the k = 1 fold (bottom-left) as the test set, k = 2 through 4 as the training set, along with a "fold buffer" extending outwards from the test set to maintain spatial independence between it and the training set.}\label{fig:scbi-spatial-cross-validation-schematic}
\end{figure}

>>>>

% Pandoc citation processing

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(lubridate)}
\KeywordTok{library}\NormalTok{(sf)}
\KeywordTok{library}\NormalTok{(patchwork)}
\KeywordTok{library}\NormalTok{(forestecology)}
\KeywordTok{library}\NormalTok{(blockCV)}

\CommentTok{# Resolve conflicting functions}
\NormalTok{filter <-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\NormalTok{filter}
\NormalTok{select <-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\NormalTok{select}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{census_}\DecValTok{2013}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem2.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \CommentTok{# Convert date from character to date}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \CommentTok{# Convert dbh to be in cm}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh) }\OperatorTok{/}\StringTok{ }\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census_}\DecValTok{2018}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"scbi.stem3.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date),}
    \DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh) }\OperatorTok{/}\StringTok{ }\DecValTok{10}
\NormalTok{  ) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(stemID, sp, dbh1, dbh2, growth, geometry)}
\CommentTok{## Simple feature collection with 7954 features and 5 fields}
\CommentTok{## Geometry type: POINT}
\CommentTok{## Dimension:     XY}
\CommentTok{## Bounding box:  xmin: 0.2 ymin: 300 xmax: 300 ymax: 600}
\CommentTok{## CRS:           NA}
\CommentTok{## # A tibble: 7,954 x 6}
\CommentTok{##   stemID sp     dbh1  dbh2 growth   geometry}
\CommentTok{##    <dbl> <fct> <dbl> <dbl>  <dbl>    <POINT>}
\CommentTok{## 1      4 nysy  13.6   14.2  0.103 (14.2 428)}
\CommentTok{## 2      5 havi   8.8    9.6  0.150  (9.4 436)}
\CommentTok{## 3      6 havi   3.25   4    0.140  (1.3 434)}
\CommentTok{## 4     77 qual  65.2   66    0.141 (34.7 307)}
\CommentTok{## 5     79 tiam  47.7   46.8 -0.161   (40 381)}
\CommentTok{## # ... with 7,949 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{sample_n}\NormalTok{(}\DecValTok{500}\NormalTok{), }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ growth)) }\OperatorTok{+}\StringTok{ }\KeywordTok{scale_size_binned}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{,}
    \DecValTok{1}\NormalTok{)) }\OperatorTok{+}\StringTok{ }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{size =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(Growth, }\StringTok{" (cm "}\NormalTok{, y}\OperatorTok{^}\NormalTok{\{}
    \DecValTok{-1}
\NormalTok{\}, }\StringTok{")"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{sp_info <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"SCBI_ForestGEO_sp_ecology.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(}\DataTypeTok{sp =}\NormalTok{ spcode, family, genus, species, canopy_position, drought_tolerance)}
\NormalTok{sp_info}
\CommentTok{## # A tibble: 65 x 6}
\CommentTok{##   sp    family        genus       species     canopy_position drought_toleran~}
\CommentTok{##   <chr> <chr>         <chr>       <chr>       <chr>           <chr>           }
\CommentTok{## 1 acne  Sapindaceae   Acer        negundo     understory      drought-resista~}
\CommentTok{## 2 acpl  Sapindaceae   Acer        platanoides canopy          drought-resista~}
\CommentTok{## 3 acru  Sapindaceae   Acer        rubrum      canopy          drought-resista~}
\CommentTok{## 4 aial  Simaroubaceae Ailanthus   altissima   canopy          drought-resista~}
\CommentTok{## 5 amar  Rosaceae      Amelanchier arborea     understory      drought-resista~}
\CommentTok{## # ... with 60 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{left_join}\NormalTok{(sp_info, }\DataTypeTok{by =} \StringTok{"sp"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{sp =} \KeywordTok{as.factor}\NormalTok{(sp))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Install development version of allodb using:}
\CommentTok{# remotes::install_github("forestgeo/allodb")}
\KeywordTok{library}\NormalTok{(allodb)}
\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \CommentTok{# Compute basal area:}
    \DataTypeTok{basal_area =} \FloatTok{0.0001} \OperatorTok{*}\StringTok{ }\NormalTok{pi }\OperatorTok{*}\StringTok{ }\NormalTok{(dbh1 }\OperatorTok{/}\StringTok{ }\DecValTok{2}\NormalTok{)}\OperatorTok{^}\DecValTok{2}\NormalTok{,}
    \CommentTok{# Compute above ground biomass:}
    \DataTypeTok{agb =} \KeywordTok{get_biomass}\NormalTok{(}
      \DataTypeTok{dbh =}\NormalTok{ dbh1,}
      \DataTypeTok{genus =}\NormalTok{ genus,}
      \DataTypeTok{species =}\NormalTok{ species,}
      \DataTypeTok{coords =} \KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{78.2}\NormalTok{, }\FloatTok{38.9}\NormalTok{)}
\NormalTok{    )}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Define competitive distance range}
\NormalTok{comp_dist <-}\StringTok{ }\FloatTok{7.5}

\CommentTok{# Manually construct study region boundary}
\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}\DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{), }\DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{,}
    \DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{sf_polygon}\NormalTok{()}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_scbi)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Manually define spatial blocks to act as folds}
\NormalTok{n_fold <-}\StringTok{ }\DecValTok{4}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{0}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{150}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold3 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{150}\NormalTok{, }\DecValTok{0}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold4 <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{150}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{450}\NormalTok{, }\DecValTok{450}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2), }\KeywordTok{sf_polygon}\NormalTok{(fold3),}
    \KeywordTok{sf_polygon}\NormalTok{(fold4)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n_fold) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{spatial_block_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}\DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =}\NormalTok{ n_fold,}
    \DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ spatial_block_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{factor}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ blocks_scbi, }\DataTypeTok{fill =} \StringTok{"transparent"}\NormalTok{, }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{) }\OperatorTok{+}
\StringTok{    }\KeywordTok{geom_sf_text}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{sample_n}\NormalTok{(}\DecValTok{1000}\NormalTok{), }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ foldID, }\DataTypeTok{col =}\NormalTok{ buffer))}
\end{Highlighting}
\end{Shaded}

@@

\caption{Schematic of spatial cross-validation. Using the k = 1 fold (bottom-left) as the test set, k = 2 through 4 as the training set, along with a fold buffer extending outwards from the test set to maintain spatial independence between it and the training set.}\label{fig:scbi-spatial-cross-validation-schematic}
\end{figure}
